Title

### 2017-05-09 paper/paper.tex
small paper changes

All algorithms and code were written using Python 3, along with numpy, SciPy, and various other Python libraries.

@@

The \texttt{TopInterval} learning algorithm was implemented true to form as presented in \cite{DBLP:journals/corr/JosephKMNR16}. Particular details of note - to ensure that all matrices used in computation were nonsingular, the first $d$ rounds are always chosen to be exploration rounds, where $d$ is the number of features. Additionally, we found it necessary to pick each arm once in order to observe data for each.

@@

@@

To expand upon the initial work done by Joseph et. al, we endeavored to test the presented algorithms on a real dataset. A Yahoo! dataset containing logs of user-visits to the front page was procured to evaluate our contextual bandits algorithms. Each log entry details the following:

@@

In a fashion similar to that presented in \cite{DBLP:journals/corr/abs-1003-5956}, we devised an evaluation scheme for the various learning algorithms. In our procedure, a random sample is drawn from the set of logged events. The learning algorithm scans through the sampled events linearly, evaluating its predictions for each one. If there happens to be a match between the algorithm's picked arm and the article displayed in the event, the logged event is added to the history.

@@

To resolve the second issue, we made a simplification to the problem context by clustering the articles. Across the million and a half logged events, there are approximately $20$ distinct articles in the article pools. In choosing a smaller number of clusters, we altered the scenario such that a successful event would be if the user clicked an article that was from the same pool chosen by the algorithm. In grouping the articles together, we reduced the number of available arms and also developed the notion of `groups' implicit in Joseph et. al.'s contextual bandits framework. The emergent notion of fairness then lies in discrimination against any particular cluster of articles.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{yahoo-interval-chaining.png}
\caption{\emph{Performance metrics of the logistic-regression based interval-chaining algorithm with $3$ clusters over 10,000 iterations. Shown on the left is a graph depicting the performance of the learning algorithm vs that of the `best' player, whose picked article is clicked by the user in every round. The regret is simply the difference in the cumulative number of successes between the two. In practice, this is an unfair comparison to make, as it is unreasonable to expect that the user would click the featured article every visit - and our results stand even stronger in comparison. On the right is a graph denoting the cumulative fraction of successful picks by the algorithm vs. the baseline (randomly selecting one out of the three pools at each step). The learning algorithm appears to converge to approximately $50\%$ accuracy, which is considerably higher than the baseline.} \label{fig:yahoo}}
\end{figure*}

>>>>

All algorithms and code were written using Python 3, along with NumPy\footnote{http://www.numpy.org}, SciPy\footnote{https://www.scipy.org}, and various other Python libraries.

@@

The \texttt{TopInterval} learning algorithm was implemented true to form as presented in \cite{DBLP:journals/corr/JosephKMNR16}. Particular details of note --- to ensure that all matrices used in computation were nonsingular, the first $d$ rounds are always chosen to be exploration rounds, where $d$ is the number of features. Additionally, we found it necessary to pick each arm once in order to observe data for each.

@@

The \texttt{RidgeFair} algorithm was also implemented as presented in (Joseph et al., 2016). This algorithm is very similar in implementation to \texttt{IntervalChaining}, save that it’s narrower confidence intervals allow for derivation of tighter regret bounds. Some details to note are that we assume for simplicity (and without loss of generality) that our parameter $R = 1$ and that we play uniformly randomly among all arms.

@@

To expand upon the initial work done by \newcite{DBLP:journals/corr/JosephKMNR16}, we endeavored to test the presented algorithms on a real dataset. A Yahoo! dataset containing logs of user-visits to the front page was procured to evaluate our contextual bandits algorithms \cite{yahoo}. Each log entry details the following:

@@

In a fashion similar to that presented in \newcite{DBLP:journals/corr/abs-1003-5956}, we devised an evaluation scheme for the various learning algorithms. In our procedure, a random sample is drawn from the set of logged events. The learning algorithm scans through the sampled events linearly, evaluating its predictions for each one. If there happens to be a match between the algorithm's picked arm and the article displayed in the event, the logged event is added to the history.

@@

To resolve the second issue, we made a simplification to the problem context by clustering the articles. Across the million and a half logged events, there are approximately $20$ distinct articles in the article pools. In choosing a smaller number of clusters, we altered the scenario such that a successful event would be if the user clicked an article that was from the same pool chosen by the algorithm. In grouping the articles together, we reduced the number of available arms and also developed the notion of ``groups" implicit in \newcite{DBLP:journals/corr/JosephKMNR16}'s contextual bandits framework. The emergent notion of fairness then lies in discrimination against any particular cluster of articles.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{yahoo-interval-chaining.png}
\caption{\emph{Performance metrics of the logistic-regression based interval-chaining algorithm with $3$ clusters over 10,000 iterations. Shown on the left is a graph depicting the performance of the learning algorithm vs that of the ``best" player, whose picked article is clicked by the user in every round. The regret is simply the difference in the cumulative number of successes between the two. In practice, this is an unfair comparison to make, as it is unreasonable to expect that the user would click the featured article every visit - and our results stand even stronger in comparison. On the right is a graph denoting the cumulative fraction of successful picks by the algorithm vs. the baseline (randomly selecting one out of the three pools at each step). The learning algorithm appears to converge to approximately $50\%$ accuracy, which is considerably higher than the baseline.} \label{fig:yahoo}}
\end{figure*}
